Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-11-04 paper/pool_model.tex
make subfigure letters not bold

        (\textbf{A}) The time dependence of the total bacterial count $N$ for the model including the back-flow to the lag phase due to temperature stress~(\ref{eq:ode_tempshift_backlag}).
        (\textbf{B}) The value of the corresponding back-flow rate $\gamma$ calculated according to (\ref{eq:gamma_tempshift}).

@@

        The growing bacteria $B$ produces toxin $T_B$ (\textbf{A}) constantly $\dot{T}_B^1 = \mathcal{F}^1 = \kappa G_B$ or (\textbf{B}) only during growth process $\dot{T}_B^2 = \mathcal{F}^2 = \kappa \alpha_B R G_B$ with

@@

        The relation between inhibition strength of species $B$ and $A$ are defined by control parameter value (\textbf{A}) $\psi$ = 1, (\textbf{B}) $\psi$ = 0.5 or (\textbf{C}) $\psi$ = 2.

@@

        (\textbf{A}) $\psi=1, \phi=1$, (\textbf{B}) $\psi=1, \phi=2$ and (\textbf{C}) $\psi=2, \phi=1$.

@@

        (\textbf{A}) A cell right before and (\textbf{B}) after a division event.

>>>>

        (A) The time dependence of the total bacterial count $N$ for the model including the back-flow to the lag phase due to temperature stress~(\ref{eq:ode_tempshift_backlag}).
        (B) The value of the corresponding back-flow rate $\gamma$ calculated according to (\ref{eq:gamma_tempshift}).

@@

        The growing bacteria $B$ produces toxin $T_B$ (A) constantly $\dot{T}_B^1 = \mathcal{F}^1 = \kappa G_B$ or (B) only during growth process $\dot{T}_B^2 = \mathcal{F}^2 = \kappa \alpha_B R G_B$ with

@@

        The relation between inhibition strength of species $B$ and $A$ are defined by control parameter value (A) $\psi$ = 1, (B) $\psi$ = 0.5 or (C) $\psi$ = 2.

@@

        (A) $\psi=1, \phi=1$, (B) $\psi=1, \phi=2$ and (C) $\psi=2, \phi=1$.

@@

        (A) A cell right before and (B) after a division event.
